---
title: "Twitter-Search"
output: html_document
---
```{r twitter search}
##### EDIT SEARCH PARAMETERS BELOW
search_term <- "Perks+Wallflower"
language <- "en"
sample_size <- 3200
##### EDIT SEARCH PARAMETERS ABOVE

source('TwitterAuth.R')

# NEXT 4 LINES LOAD LIBRARIES OF FUNCTIONS
library(twitteR)
library(tm)
library(wordcloud)
library(RColorBrewer)

####### EDIT THE NEXT LINE TO SPECIFY SEARCH
tweets_raw = searchTwitter(search_term, n=sample_size, lang=language)
####### EDIT THE PREVIOUS LINE TO SPECIFY SEARCH

############  CREATE DATA FRAME ##########################
DF = twListToDF(tweets_raw) 
# TO SAVE: write.csv(DF,file='mongodb_tweets.csv')
# TO READ: DF <- read.csv(file='mongodb_tweets.csv', sep=',', header=TRUE)
##########################################################

```

# NEXT TWO LINES REMOVES META-DATA THEN CONVERTS DATA TO A NEEDED FORMAT
tweets_text = sapply(tweets_raw, function(x) x$getText())
tweets_corpus = Corpus(VectorSource(tweets_text))

# NEXT LINE REMOVES SPECIAL CHARACTERS AVAILABLE IN OTHER LANGUAGES
tweets_transformed1 <- tm_map(tweets_corpus, 
                               content_transformer(function(x) iconv(x, to="UTF-8")))
# NEXT LINE CONVERTS EVERYTHING TO LOWER CASE
tweets_transformed2 <- tm_map(tweets_transformed1,
                              content_transformer(tolower))
# NEXT LINE REMOVES PUNCTUATION
tweets_transformed3 <- tm_map(tweets_transformed2,
                              removePunctuation)
# NEXT LINE REMOVES "STOPWORDS" LIKE "THE", "AN", "IS", "BE", ETC.
tweets_transformed4 <- tm_map(tweets_transformed3,
                              function(x) removeWords(x,stopwords()))
# NEXT LINE DRAWS WORD CLOUD
wordcloud(tweets_transformed4)


# TO EXTRACT A VECTOR OF TIME DIFFERENCES
# USE PACKAGE lubridate
# PUT THIS INTO A LOOP: dt[i] = yms_hms(DF$created[1]) - yms_hms(DF$created[i])
# Don't forget to initialize dt
# FIND A WAY TO PLOT DATA, based on what we have been doing for the last several classes.

loop: for(i in 1:3200) {dt[i] = ymd_hms(DF$created[1]) - ymd_hms(DF$created[i])}


```{r spiral graph}
library(lubridate)
library(plotly)

DF <- read.csv(file='wallflower_tweets.csv', sep=',', header=TRUE)
dtime <- rep(NA,nrow(DF))
for (i in 1:nrow(DF)) {
  dtime[i] = difftime(ymd_hms(DF$created[1]), ymd_hms(DF$created[i]), unit='days')
}

r <- dtime
theta <- r%%1*360
tweettimes = data.frame(r=r,t=theta)
p <- plot_ly(
  #plotly::hobbs, r = ~r, t = ~t, color = ~nms, alpha = 0.5, type = "scatter"
  tweettimes, r=~r, t=~t, alpha=0.5, type="scatter" 
)

layout(p, title = "Hobbs-Pearson Trials", plot_bgcolor = toRGB("grey90"))
```

